### 2019-07-12 manuscript/response.tex

Done.

\begin{quote}
--57 vague pronoun -- ``this'' (as a general rule, don't use ``this'', ``that'' etc by themselves -- follow them with the noun that they're referring to)

--use commas before ``which''; if no comma, use ``that''
\end{quote}

We reworded this whole paragraph, with the aim of providing a better explanation for how polyploidization disables gametophytic SI.

@@

\begin{quote}
--83 Nitpicky, but is it accurate to refer to this as a false-positive problem?
``False positive'' implies to me the erroneous rejection of the null, but in this case the situation is more of the null being mis-specified with respect to the question the researcher is after.
The null---no rate variation---is correctly rejected.
This section probably should include a reference to Rabosky and Goldberg.
\end{quote}

We reworded this whole paragraph and aimed to provide a better explanation of the SSE family of models.

\begin{quote}
--115 I'm uncomfortable with this way of handling multiple cytotypes.
The most commonly reported cytotype could easily not be the most common cytotype in the wild (I assume that most taxa are represented by relatively few counts), and regardless, there is biology here.
Specifically, this methodology would artificially reduce the number of ploidy changes (if a taxon is polymorphic for ploidy, there's at least one event there), and the omitted changes would be disproportionately those towards the tips of the phylogeny, so not only would rates be depressed, but the bias is of a sort that the estimation of diversification parameters is particularly sensitive to (the authors will understand why this is so).
\end{quote}

This is a part of an important broader point that we hope to clarify. 
First, it is true that chromosome number multiplicity can bias coding towards more (or less) transitions when it heavily depends on the most common cytotype. 
For the majority of species (~85\%), we did not make the ploidy call, which we instead got from the original sources of the data. In the originally sources ploidy has been classified not only most common cytotype but geographical distribution, multivalence, and/or  genome sizes. 
The remaining 15\% of the sample is what we assigned based on genus or family cytotype multiplicity. 
We cross-validated all of the assignments with the data from \citet{robertson_2011} where ploidy was assigned via a chromosome number change model using ChromEvol \citep{mayrose_2010}. 
We differ in exactly 35 species from \citet{robertson_2011} were we found a new reference or a new chromosome count. 
%
%
%B: I don't think this is quite right. It's not the "lack of diploidization parameter" but the level of organization that we are measuring that is the key objection to coding each individual mutation as a transition. The key point is that *SSE models+tip states are definitely a poor estimator of mutation rate. (Irony about its lack of accuracy at the "species" level noted.)
%rm: Classifying using a chromosome number change models only could also suffer from inflation of polyploidy events due to the lack of diploidization parameters, we found some specific species in the  \citet{robertson_2011} sample that were clearly aneuploids (one chromosome difference) that were classified as polyploids using chromosome number models, we manually corrected for those hoping to minimize obvious mistakes.

% EMMA see below:
%B: I think this should be added to clarify; as well, it is something someone should write up as a paper, because it's been a topic of review conversations for at least a decade.
Second, we are interested estimating lineage transition rates and not `events', the individual mutations to polyploid state.
Following a mutation, the outcome of an interplay between multiple evolutionary forces may or may not cause a transition. 
Coding each polyploid tissue separately (indeed, it is possible that a polyploid tissue and not individual is being scored in a study) would then confound  lineage transition and mutation on multiple levels (somatic tissue, individual, and species transition). 
Our macroevolutionary parameters would then include estimate of mutation rate as well as the lineage transition rate, with the result representing a drastic and perhaps ill-advised overestimate of the lineage transition rate.

\begin{quote}
--130 I don't follow this discussion.
There's a self-incompatible pentaploid?
How is it even sexual?
Regardless, the discussion of this pentaploid should be more clearly integrated back into the central argument here, about the absence of SI polyploids (I think that's the central argument?).
\end{quote}

%B: I edited the manuscript (methods.tex) as explained below:
We removed the discussion and simply reference a more detailed treatment of this single individual potato plant.
This observation \citet{camadro_1981} and the manifold convoluted cases by which pentaploids may be sterile are distracting, and were previously covered in \citep{robertson_2011}.
Instead, we point the reader to \citet{robertson_2011}, where the possible existence of a sterile or incompatible pentaploid, which fails to set seed following self-pollination, is discussed at some length.

@@

We appreciate this suggestion and we followed it. The main result after fitting models with symmetric vs. asymmetric rates is that the direction of the results does not change but the amount of difference amongst net diversification posterior distributions does. 
We found using Bayes factors that a model including asymmetric hidden rates is preferred over a model with equal hidden rates. 
Also,  the asymmetry in the trait rates have moderate to not support of being better than a model with equal trait transition rates.  %TODO put number.

\begin{quote}
--221  Propagation
\end{quote}

Fixed.

\begin{quote}
--I would be more comfortable if each model was run at least twice, independently, to better assess whether the MCMC has indeed converged
\end{quote}

Unfortunately, we were not able to run multiple chains for all models due to limited computer resources. 
We were, however, able to test for the convergence of  three key models using Gelman's $\hat{R}$ test statistic. 
We tested convergence with two runs of 130,000 generations (after 5,000 generations of burn-in) for models D/P (BiSSE), D/P+A/B asym (HiSSE) and ID/CD/CP+A/B asym (MuHiSSE). 
The statistics and the Gelman plots in  \ref{figure:convergencestats} show that with that number of generations the models were converging. 
We increased the number of generations for all the models that we did not test, and visually assessed the mixing of models on top of demanding ESS larger than 200 for parameters.

\begin{figure}
    \centering 
      \begin{minipage}[b]{0.33\textwidth}
    \includegraphics[width=\textwidth]{Gelmanbissenodip.pdf} 
    \end{minipage}
    \begin{minipage}[b]{0.33\textwidth}
        \includegraphics[width=\textwidth]{Gelmanhissenodipasym.pdf}
        \end{minipage}
    \begin{minipage}[b]{0.33\textwidth}
             \includegraphics[width=\textwidth]{Gelmanmuhissenodipasym.pdf}
                 \end{minipage}
    \caption{ Convergence statistics and Gelman plots for D/P (BiSSE, left), D/P+A/B asym (HiSSE, right) at the top and ID/CD/CP+A/B asym (MuHiSSE, bottom). Upper limits of Gelman's test statistics should be close to 1.0 for MCMC to be considered convergent.}
    \label{figure:convergencestats}
\end{figure}

\begin{quote}
--the use of run time as a description of the analysis seems odd to me.
As a reader, I'm not interested in the power of a given computer -- I want to know how many generations the MCMC was run for, what the ESSs are, etc.
\end{quote}

We ran each model for 200,000 generations. Unfortunately, we don't have access to more than 96 hours of computational time to increase those, but we have calculated the convergence as indicated above.

@@

\begin{quote}
-325  These analyses (by accounting for diversification) may take care of this issue, but is there a problem with these results being driven by a non-stationary process being modeled as a stationary one?
\end{quote}

This was a point worth considering, but our model does not assume stationarity. 
In Fig.~4, the contributions of each pathway are functions of time.
There, we can see both the short-term and long-term behavior.

@@

\begin{quote}
--340  Sentence fragment
\end{quote}

Fixed. % TODO

\begin{quote}
--beginning of the Discussion is perhaps unnecessary -- it's more like Introduction material
\end{quote}

[Considered.] % TODO %We can defend this on account of repeating some of the points because of numerous and complex  questions; aimed to prevent flipping pages back

@@

\begin{quote}
--are the results from the analyses that include diploidization coherent?
I'm not sure how to phrase this -- I guess I'm asking if there's any suggestion that that parameterization is indeed capturing the biological phenomenon of diploidization, or is it just soaking up noise?
\end{quote}

%B: Rosana, you know this best, but it seems to me that the current phrasing (below) is unclear.
The soaking noise comes from the hidden state so in the presence of hidden states finding that diploidization matters is key. 
All the Bayes factors indicated strong support for models that include diploidization. 
However, the diploidization parameter is difficult to estimate (wide credible intervals) mainly because diploidization is a genome size process that can be partially or minimally recover from ploidy data. 
This is the reason why we do not overstate this finding, the importance of diploidization needs to be studied using genomes.

@@

We're pleased R2 found the results interesting!

\begin{quote}
I have two ``major'' comments.
The first is relatively easy to fix and is linked to the writing/structure of the paper.
I often had the impression that too much knowledge is assumed from the reader throughout the manuscript.
For instance, more information should be given in the intro regarding why self-incompatibility breakdowns with polyploidy (it is briefly explained, but only later in the manuscript).
Moreover, some methodological approaches could be better explained.
In particular, HISSE models are relatively recent and many readers may not know them well.
I thus think that it would be important to describe them better and also better explain the results (using biological terms) obtained.
I mention some examples below in the detailed notes where I think explanations could be added.
\end{quote}

We have rewritten parts of the manuscript, especially in the Introduction, to try to explain better the relationship between polyploidy and self-incompatibility, and the interpretations of hidden state models.
% E: I labeled the two paragraphs that I modified heavily.

\begin{quote}
My second comment has to do with the parameterization of the models.
Overall, I think that the authors have done a great job in justifying their models and explaining them.
I think it is important to mention.
In addition, their implementation of the models in revBayes is noteworthy and although not stated precisely in the manuscript, I believe this represents a great scientific contribution. 
Nevertheless, I question the decision to restrict the transition rates to and from the hidden states to be all equal.
Indeed, we have no idea that could make us think that this would be the case.
The authors justify this by ``Because our goal was to look for diversification rate differences associated with ploidy and breeding system rather than the specific effects of the hidden states, we fit a simplified version with 16 parameters.''
I am not completely convinced by this argument.
First, constraining transition rates can have an impact on the estimation of diversification rates.
Second, specifically because the authors are not interested in estimating the rates themselves, they should not be too worried about increasing the number of parameters.
This is especially true in a Bayesian framework where it is sometimes better to have overparameterized models than under-parameterized models (see Lemmon and Moriarty. 2004. Systematic Biology 53:265–277).
I think it would have been important to at least present the results of an unconstrained model to show that this decision to constrain the rates do not affect the conclusions.
\end{quote}

We have now fitted models with asymmetric hidden rates and asymmetric trait rates. We found that the former are important and strengthened the differences. We found no evidence that having all asymmetric rates is preferable over just asymmetric hidden for our specific example. %TODO (Figs and table)

@@

\begin{quote}
Finally, I have a suggestion for the authors.
One thing that I would have like to see is a discussion regarding the distribution of the hidden states at the tip of the tree (e.g., Fig S6, S8).
The two peaks distributions obtained for the hidden and non-hidden states made me wonder if the high and low rate peaks could be restricted to specific clades on the phylogeny.
After inspecting the supplementary material, I see that it is not the case; hidden states are rather spread throughout the phylogeny.
I think this is interesting and that it could make an interesting discussion.
\end{quote}

Thank you for this suggestion, which we have incorporated in the Discussion. % TODO

### 2019-07-12 manuscript/discussion.tex
edits/reorg of Diploidization section of Discussion

Throughout our numerous model comparisons, models that included a hidden trait emerged as significantly better than those that did not. % supptable ref
This is entirely consistent with the expectation that many processes can affect speciation and extinction, far beyond the one or two traits of particular interest to us.
A natural follow-up question is, what is this hidden trait?
Our results show that to some extent, breeding system functions as a hidden trait in the ploidy-centered analysis, and vice versa.
But there is also strong statistical support for a hidden trait beyond ploidy and breeding system.
One temptation is to propose specific possible traits to add into the analysis.
For example, the rapidly-diversifying clade of mostly SC species within \emph{Solanum} suggests that geography may play a role. % Boris, please check!  Australian?  fixme
% alpha is always low
%   new supp fig showing how A & B are inferred on the tree?  at least for ID/CD/CP+A/B model
Alternatively, we could view the hidden trait as merely a statistical trick, providing an easy way to model extra heterogeneity without directly representing a real trait.

@@

% pathways: compare/contrast with robertson2011
%     \rho_I > \rho_C in all!

% Will: I really like the pathways analyses and have a couple comments
%
% 1) Were the "without diversification" and "with diversification" analyses computed
%    using the same MAP transition rate estimates? Transition rates among states will
%    be very different if estimated using a model that is diversification-independent 
%    compared to when estimated with a trait-dependent diversification model. Since the point of 
%    showing these side-by-side seems to be emphasizing the importance of considering trait-dependent
%    diversification, I wonder how different the "without diversification" contributions would be
%    if calculated from transition rates estimated using a diversification-independent model.
%  R- Good point. Emma will clarify
%  E: Yes, good point.  Rosana, do you have results for state-independent diversification?  We could compare with using those rates.
%
% 2) I think stochastic mapping would be another useful perspective on the pathways question
%    (and yeah, its a bit late in the game to propose analyses, so maybe next time!). With stochastic 
%    mapping we could use the entire posterior estimate of the transition rates rather than a point
%    estimate. But more importantly we'd get the relative contributions of the pathways estimated 
%    over the actual Solanceae tree (which has a lot of short interdependent branches rather than 
%    hypothetical long branches). 
%R- It will, it was actually on my code I think for the ID/CD/CP I have the stochastic mapping trees. We can do it for the revision. I think the only model where it could not finish was the ID/CD/CP+A/B (was taking forever and we had the restriction of time from MSI)

@@

% Motivated by the widespread recent findings of polyploidy in the ancestry of angiosperms, we also examined and found modest support for diploidization in the history of the family, but without significant effects on inferences of diversification dynamics. %B: how about "modest"? %R- I think modest is a good way to express it because it is the best we can do with chromosome numbers.  %B: changed "polyploidy events" (polyploidy is a noun, only. polyploid either noun or adjective).

%R: and I: polyploid lineage that has re-diploidized may enhance diversification.
%R: By adding diploidization to models of polyploidy linked to diversification it is possible to recover this complicated scenario and to reconcile genomic evidence with comparative phylogenetic models. 
%In the cases where ploidy level was assigned by us based chromosome multiplicity at the genus level, estimating diploidization  might be a potential issue due to ploidy misclassification.

%B: yielding to %R here. I still think there is overwhelming support for this statement, and few of the cited papers show convincingly that, for example, diploidization happens within five orders of magnitude compared with polyploidization, rendering "relatively rare" obsolete or invalid. (P.S. Rare not the same as unimportant!)
%B: was: Diploidization is widely considered to be relatively rare, compared with polyploidization \citep{husband_2013}, but flowering plant lineages are thought to have experienced at least one round of polyploidization in their evolutionary history \citep{soltis_2015}.
%Our exploratory analyses recover some support for inclusion of diploidization in the history of the family, but without significant effects on inferences of diversification dynamics.
%R- The line above is included in the bottom so no more need for that here
The implications of the results of our diploidization analyses, as well as much of the other recent work on WGDs, are interesting because they conflict with other lines of evidence, especially those concerning the observed simple synteny of genomes in Solanaceae, and patterns of evolution at self-incompatibility loci.
Flowering plant lineages are thought to have experienced at least one round of polyploidization in their evolutionary history \citep{soltis_2015}. 
Following polyploidization, it is possible for genome reorganization, downsizing, and loss to occur \citep{dodsworth_2015, zenil_2016, mandakova_2018}. %B: commas, etc.: importantly rm: "has been observed" this is _only_ true on very short time scales
As a consequence, nearly all extant species classified as ``diploid" in our analyses, based on cytogenetic data, are possibly secondary diploids, having undergone both polyploidization and re-diploidization.
Unduly ignoring secondary diploidization would necessarily underestimate the rate of transitions from polyploids to diploids.
It would then likely cause inflated net diversification rates for diploids, because species considered diploid may have been ancestrally polyploid, instead. %B: added before conflict/edits
%We find strong support for including the diploidization rate parameter ($\delta$) in analyses that include only ploidy . %B <- %Rosana, inspect this please. It's a merge of conflicted lines.
% R- I put it up so the line above is not necessary anymore
However, we find only modest support for diploidization in the joint model  (\cref{table:bayesfactors}), and conclusions regarding the relative effects of ploidy and breeding system on diversification are robust to its inclusion.
Furthermore, estimating the rate of diploidization, based on our ploidy level classifications, is highly uncertain (see parameter $\delta$ in \cref{suppfigure:DP,suppfigure:DPAB,suppfigure:IDCDCP,suppfigure:IDCDCPAB}), and yields dramatic changes in ancestral reconstructions (\cref{suppfigure:DPnodipasr,suppfigure:DPasr,suppfigure:DPnodipABasr,suppfigure:DPABasr,suppfigure:IDCDCPnodipasr,suppfigure:IDCDCPasr,suppfigure:IDCDCPnodipABasr,suppfigure:IDCDCPABasr}).

Some lines of evidence indicate that polyploidy may have occurred prior to the origin of Solanaceae, rendering all extant `diploids' secondarily derived. %B: "polyploid event" or "polyploidy" works, but not "polyploidy event"; see above.
First, \citet{ku2000} and \citet{blanc2004} posited that the lineage leading to tomato, \textit{Solanum lycopersicum}, may have experienced one or more of WGDs.
A subsequent analysis of synteny between grape and \textit{Solanum} genomes, as well as the distribution between inferred paralogs within genomes of \textit{Solanum} (tomato and potato) each suggested that this lineage experienced a likely round of ancient genome duplication or triplication \citep{tomato2012}. 
The age of the peak of paralog Ks distances is approximately 71$\pm$19 My \citep{tomato2012}. 
If this is the case, then all of the genomes may have been subsequently re-diploidized, yielding the widespread and common chromosome numbers in this and related families, n=11--12, presently considered to be diploid \citep{robertson_2011}.

On the other hand, there is little evidence for the occurrence of re-diploidization within Solanaceae, since the origin of the family---the time frame we considered.
First, the Ks-inferred duplication likely pre-dates the origin of the family (49 My, HPD 46--53 My \citealt{sarkinen_2013}). 
The best-supported, most-recent WGD \citep{tomato2012} is older than the clade under consideration in this study.
At best then, the species we consider are ancestrally diploid, having re-diploidized after a suspected WGD, but likely before the origin of the family.
Second, studies comparing map-based genome synteny within the family find no evidence for recent diploidization \citep{wu_2010a}.
Instead, simple genome re-arrangements appear sufficient to explain chromosomal evolution between a number of species, including all of those in the relatively cytogenetically conserved `x=12' group, which includes tomato, potato, eggplant, pepper, and tobacco.
Despite the limitations of assignment of ploidy levels, we found some support for models that include parameter $\delta$, meaning that further study may be warranted, especially in other groups.

Regardless of whether genome polypoidization, followed by widespread diploidization, is a dominant mechanism of genome evolution in Solanaceae, it is clear that our present understanding of the evolution of ploidy and breeding systems is incomplete.
An increasingly forceful weight of evidence seems to support WGDs in the ancestry of many angiosperms. %cite
It is then easily inferred that many species have undergone diploidization, alongside genome size and chromosome number reductions. %cite
Inference of such a common genome upheaval in eudicot history seems to clash with the data indicating that a homologous mechanism of SI, which breaks down nearly invariably in natural and induced tetraploids \citep{stone_2002,mcclure_2009}, has been present continually in many families, including Solanaceae \citep{igic_2006}. 
Most problematically in this context, it is unclear how to explain the maintenance of trans-generic polymorphism at the orthologous S-loci in this and other families.
As well, chromosome numbers and genome comparisons within the family (esp.\ `x=12' clade, containing \textit{Solanum} and \textit{Nicotiana}) reveal strong conservation.
\citet{wu_2010a} review the evidence from map-based genome comparisons and find that tomato and potato differ by six inversions, tomato and eggplant by 24 inversions and five translocations, tomato and pepper by 19 inversions and six translocations, and tomato and tobacco by ca.\ 10 inversions and 11 translocations (likely underestimated).
Recovery of such simple relationships would require outstanding convergent loss of duplicated segments.
In either case, all of the approaches make ample assumptions, and it seems that at least some of them will necessitate deep revisions.
Our study, for example, made numerous assumptions in coding trait states (\eg what constitutes a polyploid or diploid, SI or SC species), in models used for analyses (\eg irreversibility of SI loss underlain by trans-specific orthologous S-loci), and many more, which could each mislead inference. %B: -> %R: Rosana, take a look at this.
% no discussion of magnitude of \delta vs \rho!
% R- magnitude is not easy to discuss about, what we have are estimates and credible intervals which are completely sample size dependent. With a different sample "magnitude" can change.
% problems: this system has a big set of advantages - carefully curated (co-)occurrences of two traits, genetic basis, etc. and everything is still contradictory and opaque.

@@

%B: Rosana, read this carefully, please! I think it may need review:
%B: I changed nothing here, except: (1) a citealt<-citet to avoid double parentheses. (2) sp. disscussed -> discussed, (3) "If that is the case ON a system" -> "... IN a system"? (4) "hight type I errors" -> high, type I errors [comma], (5) line break in penultimate sentence.
Estimating rates of trait linked diversification models is not only a problem of difficult parametric inference (as discussed in \citealt{rabosky_2010, beaulieu_2015}), but also a problem of inadequate ``*SSE'' model specification that can result in misleading inferences when the presence of a second trait has a complex interaction with the focal trait first used to model diversification. 
We presented a roadmap with a series of analyses that can identify whether unknown or unobservable traits are worth pursuing. 
In this roadmap, we have proposed fitting HiSSE models that have effectively shown that some binary states associated with diversification under BiSSE analyses are actually not different in net diversification terms, and instead a hidden state is linked to differences in the diversification rate \citep{beaulieu_2016}.  
If that is the case in a study system, raising the question of the identity of the hidden state should be considered as the next step in the modeling process.  % E: I would say not necessarily.  There could be other non-trait weirdnesses.  TODO: include a more comprehensive discussion of how to interpret hisse/hidden state
When considering a second candidate trait, one can model the complex interactions via a MuSSE model, especially in systems where multiple traits are suspected to influence diversification, and where interactions between those traits are well understood. 
Since MuSSE can also falsely associate traits with diversification \citep{fitzjohn_2012}, considering more heterogeneity using a hidden state model on top of the multi-state diversification model is necessary to adequately infer the effect of the complex interactions in the speciation and extinction process.
% R- new lines
Investigating the process of diversification linked to traits can be done via thorough statistical inferences that carefully evaluate multiple evolutionary histories. 
Background heterogeneity in lineage of diversification is the rule, rather than the exception. 
Inferences that question whether other complex trait interactions are hidden in this background heterogeneity are necessary because they critically contribute to the reconstruction and understanding of diversification.

%%%%%%%%%%
% E notes:
%
% summarize div findings
%     breeding system takes from ploidy
%     but not simple SI/SC pattern
% what is the hidden state?
%     could be a real trait, see tip ASR, geography?
%     but don't be circular, test in different clade
%     could be a stats trick
%
% pathways
%     likely way to lose SI
%     likely way to become P
%     (compare those relative rates with robertson2011)
%     different consequences for eventual D?
%     div effects on pathway commonness
%     path-dep div in CP?
%     clado
%
% diploidization
%     some model support
%     but still SC
% paleopolyploidy
%     if before root, no SI?

>>>>

Throughout our numerous model comparisons, models that included a hidden trait emerged as significantly better than those that did not. % supptable ref
This is entirely consistent with the expectation that many processes can affect speciation and extinction, far beyond the one or two traits of particular interest to us.
A natural follow-up question is, what is this hidden trait?
Our results show that to some extent, breeding system functions as a hidden trait in the ploidy-centered analysis, and vice versa.
But there is also strong statistical support for a hidden trait beyond ploidy and breeding system.
One temptation is to propose specific possible traits to add into the analysis.
For example, the rapidly-diversifying clade of mostly SC species within \emph{Solanum} suggests that geography may play a role. % Boris, please check!  Australian?  fixme
%     but don't be circular, test in different clade
% alpha is always low: new supp fig showing how A & B are inferred on the tree?  at least for ID/CD/CP+A/B model
Alternatively, we could view the hidden trait as merely a statistical trick, providing an easy way to model extra heterogeneity without directly representing a real trait.

@@

% pathways: compare/contrast with robertson2011
%     \rho_I > \rho_C in all!
%     likely way to lose SI
%     likely way to become P
%     (compare those relative rates with robertson2011)

@@

Polyploidization is known to be common in plants, but the commonness of the reverse process---diploidization---is under active investigation.
%
In our analyses, ignoring diploidization if it is common could cause us to underestimate the polyploidization rate, overestimate of the diploid diversification rate, or otherwise confound our conclusions.
We therefore included a slate of models with a diploidization parameter, and they showed that our main conclusions are robust to this process.
These models also suggested modest statistical support for diploidization occuring within Solanaceae \cref{supptableFIXME}, although our estimates of the diploidization rate were highly uncertain.
Furthermore, additional lines of evidence for classifying species as diploid or polyploid (beyond the genus chromosome multiplicity that we primarily relied on) would be needed for more reliable conclusions from an analysis such as ours.
%In the cases where ploidy level was assigned by us based chromosome multiplicity at the genus level, estimating diploidization might be a potential issue due to ploidy misclassification.  
%R: By adding diploidization to models of polyploidy linked to diversification it is possible to recover this complicated scenario and to reconcile genomic evidence with comparative phylogenetic models. 
%B: yielding to %R here. I still think there is overwhelming support for this statement, and few of the cited papers show convincingly that, for example, diploidization happens within five orders of magnitude compared with polyploidization, rendering "relatively rare" obsolete or invalid. (P.S. Rare not the same as unimportant!)
%B: was: Diploidization is widely considered to be relatively rare, compared with polyploidization \citep{husband_2013}, but flowering plant lineages are thought to have experienced at least one round of polyploidization in their evolutionary history \citep{soltis_2015}.

% E: Boris, could you please revisit the following two paragraphs?  TODO
% Two questions:
%    Did my reorganization of this section mess anything up?
%    Can this text be shorter?  It's seems disproportionately long, and I'm hesitant to revise it heavily myself because the logical connections aren't entirely clear to me.

Other lines of evidence about the prevalence of diploidization within Solanaceae or its ancestors are mixed or even conflicting.
% recent work on WGDs conflict with other lines of evidence, especially those concerning the observed simple synteny of genomes in Solanaceae, and patterns of evolution at self-incompatibility loci
%
% Part I: evidence for WGD in/near family
On the one hand, polyploidy may have occurred prior to the origin of Solanaceae, rendering all extant `diploids' secondarily derived.
\Citet{ku2000} and \citet{blanc2004} posited that the lineage leading to tomato, \emph{Solanum lycopersicum}, may have experienced one or more whole genome duplications.
A subsequent analysis of synteny between grape and \emph{Solanum} genomes, as well as the distribution between inferred paralogs within genomes of \emph{Solanum} (tomato and potato) each suggested that this lineage experienced a likely round of ancient genome duplication or triplication \citep{tomato2012}. 
The age of the peak of paralog Ks distances is approximately $71 \pm 19$ My \citep{tomato2012}. 
If this is the case, then all of the genomes may have been subsequently diploidized, yielding the widespread and common chromosome numbers in this and related families, n=11--12, presently considered to be diploid \citep{robertson_2011}.

% Part II: evidence against WGD in/near family
On the other hand, there is little evidence for the occurrence of diploidization within Solanaceae itself.
First, the Ks-inferred duplication \citep{tomato2012} likely pre-dates the origin of the family (49 My, HPD 46--53 My; \citealt{sarkinen_2013}). 
Thus, the species in our analyes could be ancestrally polyploid, but would have diploidized before the root of the family.
Second, studies comparing map-based genome synteny within the family find no evidence for recent diploidization \citep{wu_2010a}.
Instead, simple genome re-arrangements appear sufficient to explain chromosomal evolution between a number of species. % including all of those in the relatively cytogenetically conserved x=12 group, which includes tomato, potato, eggplant, pepper, and tobacco.
Specifically, chromosome numbers and genome comparisons within the family (esp.\ the x=12 clade containing \textit{Solanum} and \textit{Nicotiana}) reveal strong conservation.
\citet{wu_2010a} review the evidence from map-based genome comparisons and find that tomato and potato differ by six inversions, tomato and eggplant by 24 inversions and five translocations, tomato and pepper by 19 inversions and six translocations, and tomato and tobacco by ca.\ 10 inversions and 11 translocations (likely underestimated).
Recovery of such simple relationships would require outstanding convergent loss of duplicated segments.
%
% Part IIb: evidence from SI [might need more explaining?]
Furthermore, whole genome duplication in a eudicot lineage ancestral to Solanaceae would clash with the evidence that the homologous mechanism of SI that has been present continually in many families \citep{igic_2006} breaks down nearly invariably in natural and induced tetraploids \citep{stone_2002, mcclure_2009}.
Most problematically in this context, it is unclear how to explain the maintenance of trans-generic polymorphism at the orthologous S-loci in Solanaceae and other families if SI was previously broken down by polyploidization.
%
Regardless of whether genome polypoidization, followed by widespread diploidization, is a dominant mechanism of genome evolution in Solanaceae, it is clear that more work is needed for a complete understanding of the joint evolution of ploidy and breeding systems.

% Flowering plant lineages are thought to have experienced at least one round of polyploidization in their evolutionary history \citep{soltis_2015}. 
% Following polyploidization, it is possible for genome reorganization, downsizing, and loss to occur \citep{dodsworth_2015, zenil_2016, mandakova_2018}.
% As a consequence, nearly all extant species classified as ``diploid" in our analyses are possibly secondary diploids, having undergone both polyploidization and subsequent diploidization.

% no discussion of magnitude of \delta vs \rho!

% problems: this system has a big set of advantages - carefully curated (co-)occurrences of two traits, genetic basis, etc. and everything is still contradictory and opaque.

@@

%B: Rosana, read this carefully, please! I think it may need review:
%B: I changed nothing here, except: (1) a citealt<-citet to avoid double parentheses. (2) sp. disscussed -> discussed, (3) "If that is the case ON a system" -> "... IN a system"? (4) "hight type I errors" -> high, type I errors [comma], (5) line break in penultimate sentence.
Estimating rates of trait linked diversification models is not only a problem of difficult parametric inference (as discussed in \citealt{rabosky_2010, beaulieu_2015}), but also a problem of inadequate SSE model specification that can result in misleading inferences when the presence of a second trait has a complex interaction with the focal trait first used to model diversification. 
We presented a roadmap with a series of analyses that can identify whether unknown or unobservable traits are worth pursuing. 
In this roadmap, we have proposed fitting HiSSE models that have effectively shown that some binary states associated with diversification under BiSSE analyses are actually not different in net diversification terms, and instead a hidden state is linked to differences in the diversification rate \citep{beaulieu_2016}.  
If that is the case in a study system, raising the question of the identity of the hidden state should be considered as the next step in the modeling process.  % E: I would say not necessarily.  There could be other non-trait weirdnesses.  TODO: include a more comprehensive discussion of how to interpret hisse/hidden state
When considering a second candidate trait, one can model the complex interactions via a MuSSE model, especially in systems where multiple traits are suspected to influence diversification, and where interactions between those traits are well understood. 
Since MuSSE can also falsely associate traits with diversification \citep{fitzjohn_2012}, considering more heterogeneity using a hidden state model on top of the multi-state diversification model is necessary to adequately infer the effect of the complex interactions in the speciation and extinction process.
% R- new lines
Investigating the process of diversification linked to traits can be done via thorough statistical inferences that carefully evaluate multiple evolutionary histories. 
Background heterogeneity in lineage of diversification is the rule, rather than the exception. 
Inferences that question whether other complex trait interactions are hidden in this background heterogeneity are necessary because they critically contribute to the reconstruction and understanding of diversification.
